# Reading in Overall Data
```{r, echo=FALSE}

BRTotal <- read.csv("2019_20_BRTotal.csv")
# Changing a few variable names
BRTotal <- BRTotal %>% rename(Player = ï..Player,
                              FG_P = FG.,
                              FT_P = FT.,
                              X3P_P = X3P.,
                              X2P_P = X2P.,
                              eFG_P = eFG.)
```

# PG Overall Stats
``` {r pg.overall}
#Finding the Stats for PGs
PG_Data <- BRTotal %>% filter(Pos == "PG") %>% drop_na()
# Adding the absolute value Differentials for each player from the medians
PG_Data <- PG_Data %>%
            mutate(Age.Diff = abs(PG_Data$Age - median(PG_Data$Age)),
                   G.Diff = abs(PG_Data$G - median(PG_Data$G)),
                   GS.Diff = abs(PG_Data$GS - median(PG_Data$GS)),
                   MP.Diff = abs(PG_Data$MP - median(PG_Data$MP)),
                   FG.Diff = abs(PG_Data$FG - median(PG_Data$FG)), 
                   FGA.Diff = abs(PG_Data$FGA - median(PG_Data$FGA)),
                   X3P.Diff = abs(PG_Data$X3P - median(PG_Data$X3P)),
                   X3PA.Diff = abs(PG_Data$X3PA- median(PG_Data$X3PA)),
                   X2P.Diff = abs(PG_Data$X2P - median(PG_Data$X2P)),
                   X2PA.Diff =abs(PG_Data$X2PA - median(PG_Data$X2PA)),
                   FT.Diff = abs(PG_Data$FT - median(PG_Data$FT)),
                   FTA.Diff =abs(PG_Data$FTA - median(PG_Data$FTA)),
                   TRB.Diff =abs(PG_Data$TRB - median(PG_Data$TRB)),
                   AST.Diff =abs(PG_Data$AST - median(PG_Data$AST)), 
                   STL.Diff =abs(PG_Data$STL - median(PG_Data$STL)), 
                   BLK.Diff =abs(PG_Data$BLK - median(PG_Data$BLK)),
                   TOV.Diff =abs(PG_Data$TOV - median(PG_Data$TOV)),
                   PF.Diff =abs(PG_Data$PF - median(PG_Data$PF)),
                   PTS.Diff =abs(PG_Data$PTS - median(PG_Data$PTS)),
                   FG_P.Diff =abs(PG_Data$FG_P - median(PG_Data$FG_P)),
                   FT_P.Diff =abs(PG_Data$FT_P - median(PG_Data$FT_P)),
                   X3P_P.Diff =abs(PG_Data$X3P_P - median(PG_Data$X3P_P)),
                   X2P_P.Diff =abs(PG_Data$X2P_P - median(PG_Data$X2P_P)),
                   eFG_P.Diff =abs(PG_Data$eFG_P - median(PG_Data$eFG_P)), 
                   ORB.Diff = abs(PG_Data$ORB - median(PG_Data$ORB)),
                   DRB.Diff = abs(PG_Data$DRB - median(PG_Data$DRB))
                   )
# Restructuring of Columns to make columns related to one another next to one another
PG_Data <- PG_Data %>%
  select(Player, Pos, Tm, Age, Age.Diff, G, G.Diff, GS, GS.Diff, MP, MP.Diff, FG, FG.Diff, FGA, FGA.Diff, X3P, X3P.Diff, X3PA, X3PA.Diff, X2P, X2P.Diff, X2PA, X2PA.Diff, FT, FT.Diff, FTA, FTA.Diff, TRB, TRB.Diff, AST, AST.Diff, STL, STL.Diff, BLK, BLK.Diff, TOV, TOV.Diff, PF, PF.Diff, PTS, PTS.Diff, FG_P, FG_P.Diff, FT_P, FT_P.Diff, X3P_P, X3P_P.Diff, X2P_P, X2P_P.Diff, eFG_P, eFG_P.Diff, ORB, ORB.Diff, DRB, DRB.Diff)

```

# PG Stats Per Game

```{r pg.g, echo=FALSE}
#Creating a dataframe with the data divided by Games Played
PG_Filter_G <- select(PG_Data,MP:DRB.Diff) 

PG_Stats_G <- PG_Filter_G %>% mutate_if(is.numeric, funs(./PG_Data$G))

PG_Data_G <- PG_Stats_G %>%
            mutate(MP.Diff = abs(PG_Stats_G$MP - median(PG_Stats_G$MP)),
                   FG.Diff = abs(PG_Stats_G$FG - median(PG_Stats_G$FG)), 
                   FGA.Diff = abs(PG_Stats_G$FGA - median(PG_Stats_G$FGA)),
                   X3P.Diff = abs(PG_Stats_G$X3P - median(PG_Stats_G$X3P)),
                   X3PA.Diff = abs(PG_Stats_G$X3PA- median(PG_Stats_G$X3PA)),
                   X2P.Diff = abs(PG_Stats_G$X2P - median(PG_Stats_G$X2P)),
                   X2PA.Diff =abs(PG_Stats_G$X2PA - median(PG_Stats_G$X2PA)),
                   FT.Diff = abs(PG_Stats_G$FT - median(PG_Stats_G$FT)),
                   FTA.Diff =abs(PG_Stats_G$FTA - median(PG_Stats_G$FTA)),
                   TRB.Diff =abs(PG_Stats_G$TRB - median(PG_Stats_G$TRB)),
                   AST.Diff =abs(PG_Stats_G$AST - median(PG_Stats_G$AST)), 
                   STL.Diff =abs(PG_Stats_G$STL - median(PG_Stats_G$STL)), 
                   BLK.Diff =abs(PG_Stats_G$BLK - median(PG_Stats_G$BLK)),
                   TOV.Diff =abs(PG_Stats_G$TOV - median(PG_Stats_G$TOV)),
                   PF.Diff =abs(PG_Stats_G$PF - median(PG_Stats_G$PF)),
                   PTS.Diff =abs(PG_Stats_G$PTS - median(PG_Stats_G$PTS)),
                   FG_P.Diff =abs(PG_Stats_G$FG_P - median(PG_Stats_G$FG_P)),
                   FT_P.Diff =abs(PG_Stats_G$FT_P - median(PG_Stats_G$FT_P)),
                   X3P_P.Diff =abs(PG_Stats_G$X3P_P - median(PG_Stats_G$X3P_P)),
                   X2P_P.Diff =abs(PG_Stats_G$X2P_P - median(PG_Stats_G$X2P_P)),
                   eFG_P.Diff =abs(PG_Stats_G$eFG_P - median(PG_Stats_G$eFG_P)), 
                   ORB.Diff = abs(PG_Stats_G$ORB - median(PG_Stats_G$ORB)),
                   DRB.Diff = abs(PG_Stats_G$DRB - median(PG_Stats_G$DRB))
                   )
# Restructuring of Columns to make columns related to one another next to one another
PG_Data_G <- mutate(PG_Data_G, 
                    Player = PG_Data$Player, 
                    Pos = PG_Data$Pos, 
                    Tm = PG_Data$Tm, 
                    Age = PG_Data$Age, 
                    Age.Diff = PG_Data$Age.Diff, 
                    G = PG_Data$G, 
                    G.Diff = PG_Data$G.Diff, 
                    GS = PG_Data$GS, 
                    GS.Diff = PG_Data$GS.Diff
                    )

PG_Data_G <- PG_Data_G %>%
  select(Player, Pos, Tm, Age, Age.Diff, G, G.Diff, GS, GS.Diff, MP, MP.Diff, FG, FG.Diff, FGA, FGA.Diff, X3P, X3P.Diff, X3PA, X3PA.Diff, X2P, X2P.Diff, X2PA, X2PA.Diff, FT, FT.Diff, FTA, FTA.Diff, TRB, TRB.Diff, AST, AST.Diff, STL, STL.Diff, BLK, BLK.Diff, TOV, TOV.Diff, PF, PF.Diff, PTS, PTS.Diff, FG_P, FG_P.Diff, FT_P, FT_P.Diff, X3P_P, X3P_P.Diff, X2P_P, X2P_P.Diff, eFG_P, eFG_P.Diff, ORB, ORB.Diff, DRB, DRB.Diff)
```

# PG Stats Per Minutes Played

```{r pg.mp, echo=FALSE}
#Creating a dataframe with the data divided by Minutes Played
PG_Filter_MP <- select(PG_Data,FG:DRB.Diff) 

PG_Stats_MP <- PG_Filter_MP %>% mutate_if(is.numeric, funs(./PG_Data$MP))

PG_Data_MP <- PG_Stats_MP %>%
            mutate(FG.Diff = abs(PG_Stats_MP$FG - median(PG_Stats_MP$FG)), 
                   FGA.Diff = abs(PG_Stats_MP$FGA - median(PG_Stats_MP$FGA)),
                   X3P.Diff = abs(PG_Stats_MP$X3P - median(PG_Stats_MP$X3P)),
                   X3PA.Diff = abs(PG_Stats_MP$X3PA- median(PG_Stats_MP$X3PA)),
                   X2P.Diff = abs(PG_Stats_MP$X2P - median(PG_Stats_MP$X2P)),
                   X2PA.Diff =abs(PG_Stats_MP$X2PA - median(PG_Stats_MP$X2PA)),
                   FT.Diff = abs(PG_Stats_MP$FT - median(PG_Stats_MP$FT)),
                   FTA.Diff =abs(PG_Stats_MP$FTA - median(PG_Stats_MP$FTA)),
                   TRB.Diff =abs(PG_Stats_MP$TRB - median(PG_Stats_MP$TRB)),
                   AST.Diff =abs(PG_Stats_MP$AST - median(PG_Stats_MP$AST)), 
                   STL.Diff =abs(PG_Stats_MP$STL - median(PG_Stats_MP$STL)), 
                   BLK.Diff =abs(PG_Stats_MP$BLK - median(PG_Stats_MP$BLK)),
                   TOV.Diff =abs(PG_Stats_MP$TOV - median(PG_Stats_MP$TOV)),
                   PF.Diff =abs(PG_Stats_MP$PF - median(PG_Stats_MP$PF)),
                   PTS.Diff =abs(PG_Stats_MP$PTS - median(PG_Stats_MP$PTS)),
                   FG_P.Diff =abs(PG_Stats_MP$FG_P - median(PG_Stats_MP$FG_P)),
                   FT_P.Diff =abs(PG_Stats_MP$FT_P - median(PG_Stats_MP$FT_P)),
                   X3P_P.Diff =abs(PG_Stats_MP$X3P_P - median(PG_Stats_MP$X3P_P)),
                   X2P_P.Diff =abs(PG_Stats_MP$X2P_P - median(PG_Stats_MP$X2P_P)),
                   eFG_P.Diff =abs(PG_Stats_MP$eFG_P - median(PG_Stats_MP$eFG_P)), 
                   ORB.Diff = abs(PG_Stats_MP$ORB - median(PG_Stats_MP$ORB)),
                   DRB.Diff = abs(PG_Stats_MP$DRB - median(PG_Stats_MP$DRB))
                   )
# Restructuring of Columns to make columns related to one another next to one another
PG_Data_MP <- mutate(PG_Data_MP, 
                    Player = PG_Data$Player, 
                    Pos = PG_Data$Pos, 
                    Tm = PG_Data$Tm, 
                    Age = PG_Data$Age, 
                    Age.Diff = PG_Data$Age.Diff, 
                    G = PG_Data$G, 
                    G.Diff = PG_Data$G.Diff, 
                    GS = PG_Data$GS, 
                    GS.Diff = PG_Data$GS.Diff,
                    MP = PG_Data$MP, 
                    MP.Diff = PG_Data$MP.Diff
                    )

PG_Data_MP <- PG_Data_MP %>%
  select(Player, Pos, Tm, Age, Age.Diff, G, G.Diff, GS, GS.Diff, MP, MP.Diff, FG, FG.Diff, FGA, FGA.Diff, X3P, X3P.Diff, X3PA, X3PA.Diff, X2P, X2P.Diff, X2PA, X2PA.Diff, FT, FT.Diff, FTA, FTA.Diff, TRB, TRB.Diff, AST, AST.Diff, STL, STL.Diff, BLK, BLK.Diff, TOV, TOV.Diff, PF, PF.Diff, PTS, PTS.Diff, FG_P, FG_P.Diff, FT_P, FT_P.Diff, X3P_P, X3P_P.Diff, X2P_P, X2P_P.Diff, eFG_P, eFG_P.Diff, ORB, ORB.Diff, DRB, DRB.Diff)
```
# SG Overall Stats

``` {r sg.overall}
#Finding the Stats for PGs
SG_Data <- BRTotal %>% filter(Pos == "SG") %>% drop_na()
# Adding the absolute value Differentials for each player from the medians
SG_Data <- SG_Data %>%
            mutate(Age.Diff = abs(SG_Data$Age - median(SG_Data$Age)),
                   G.Diff = abs(SG_Data$G - median(SG_Data$G)),
                   GS.Diff = abs(SG_Data$GS - median(SG_Data$GS)),
                   MP.Diff = abs(SG_Data$MP - median(SG_Data$MP)),
                   FG.Diff = abs(SG_Data$FG - median(SG_Data$FG)), 
                   FGA.Diff = abs(SG_Data$FGA - median(SG_Data$FGA)),
                   X3P.Diff = abs(SG_Data$X3P - median(SG_Data$X3P)),
                   X3PA.Diff = abs(SG_Data$X3PA- median(SG_Data$X3PA)),
                   X2P.Diff = abs(SG_Data$X2P - median(SG_Data$X2P)),
                   X2PA.Diff =abs(SG_Data$X2PA - median(SG_Data$X2PA)),
                   FT.Diff = abs(SG_Data$FT - median(SG_Data$FT)),
                   FTA.Diff =abs(SG_Data$FTA - median(SG_Data$FTA)),
                   TRB.Diff =abs(SG_Data$TRB - median(SG_Data$TRB)),
                   AST.Diff =abs(SG_Data$AST - median(SG_Data$AST)), 
                   STL.Diff =abs(SG_Data$STL - median(SG_Data$STL)), 
                   BLK.Diff =abs(SG_Data$BLK - median(SG_Data$BLK)),
                   TOV.Diff =abs(SG_Data$TOV - median(SG_Data$TOV)),
                   PF.Diff =abs(SG_Data$PF - median(SG_Data$PF)),
                   PTS.Diff =abs(SG_Data$PTS - median(SG_Data$PTS)),
                   FG_P.Diff =abs(SG_Data$FG_P - median(SG_Data$FG_P)),
                   FT_P.Diff =abs(SG_Data$FT_P - median(SG_Data$FT_P)),
                   X3P_P.Diff =abs(SG_Data$X3P_P - median(SG_Data$X3P_P)),
                   X2P_P.Diff =abs(SG_Data$X2P_P - median(SG_Data$X2P_P)),
                   eFG_P.Diff =abs(SG_Data$eFG_P - median(SG_Data$eFG_P)), 
                   ORB.Diff = abs(SG_Data$ORB - median(SG_Data$ORB)),
                   DRB.Diff = abs(SG_Data$DRB - median(SG_Data$DRB))
                   )
# Restructuring of Columns to make columns related to one another next to one another
SG_Data <- SG_Data %>%
  select(Player, Pos, Tm, Age, Age.Diff, G, G.Diff, GS, GS.Diff, MP, MP.Diff, FG, FG.Diff, FGA, FGA.Diff, X3P, X3P.Diff, X3PA, X3PA.Diff, X2P, X2P.Diff, X2PA, X2PA.Diff, FT, FT.Diff, FTA, FTA.Diff, TRB, TRB.Diff, AST, AST.Diff, STL, STL.Diff, BLK, BLK.Diff, TOV, TOV.Diff, PF, PF.Diff, PTS, PTS.Diff, FG_P, FG_P.Diff, FT_P, FT_P.Diff, X3P_P, X3P_P.Diff, X2P_P, X2P_P.Diff, eFG_P, eFG_P.Diff, ORB, ORB.Diff, DRB, DRB.Diff)
```

# SG Stats Per Game

```{r sg.g, echo=FALSE}
#Creating a dataframe with the data divided by Games Played
SG_Filter_G <- select(SG_Data,MP:DRB.Diff) 

SG_Stats_G <- SG_Filter_G %>% mutate_if(is.numeric, funs(./SG_Data$G))

SG_Data_G <- SG_Stats_G %>%
            mutate(MP.Diff = abs(SG_Stats_G$MP - median(SG_Stats_G$MP)),
                   FG.Diff = abs(SG_Stats_G$FG - median(SG_Stats_G$FG)), 
                   FGA.Diff = abs(SG_Stats_G$FGA - median(SG_Stats_G$FGA)),
                   X3P.Diff = abs(SG_Stats_G$X3P - median(SG_Stats_G$X3P)),
                   X3PA.Diff = abs(SG_Stats_G$X3PA- median(SG_Stats_G$X3PA)),
                   X2P.Diff = abs(SG_Stats_G$X2P - median(SG_Stats_G$X2P)),
                   X2PA.Diff =abs(SG_Stats_G$X2PA - median(SG_Stats_G$X2PA)),
                   FT.Diff = abs(SG_Stats_G$FT - median(SG_Stats_G$FT)),
                   FTA.Diff =abs(SG_Stats_G$FTA - median(SG_Stats_G$FTA)),
                   TRB.Diff =abs(SG_Stats_G$TRB - median(SG_Stats_G$TRB)),
                   AST.Diff =abs(SG_Stats_G$AST - median(SG_Stats_G$AST)), 
                   STL.Diff =abs(SG_Stats_G$STL - median(SG_Stats_G$STL)), 
                   BLK.Diff =abs(SG_Stats_G$BLK - median(SG_Stats_G$BLK)),
                   TOV.Diff =abs(SG_Stats_G$TOV - median(SG_Stats_G$TOV)),
                   PF.Diff =abs(SG_Stats_G$PF - median(SG_Stats_G$PF)),
                   PTS.Diff =abs(SG_Stats_G$PTS - median(SG_Stats_G$PTS)),
                   FG_P.Diff =abs(SG_Stats_G$FG_P - median(SG_Stats_G$FG_P)),
                   FT_P.Diff =abs(SG_Stats_G$FT_P - median(SG_Stats_G$FT_P)),
                   X3P_P.Diff =abs(SG_Stats_G$X3P_P - median(SG_Stats_G$X3P_P)),
                   X2P_P.Diff =abs(SG_Stats_G$X2P_P - median(SG_Stats_G$X2P_P)),
                   eFG_P.Diff =abs(SG_Stats_G$eFG_P - median(SG_Stats_G$eFG_P)), 
                   ORB.Diff = abs(SG_Stats_G$ORB - median(SG_Stats_G$ORB)),
                   DRB.Diff = abs(SG_Stats_G$DRB - median(SG_Stats_G$DRB))
                   )
# Restructuring of Columns to make columns related to one another next to one another
SG_Data_G <- mutate(SG_Data_G, 
                    Player = SG_Data$Player, 
                    Pos = SG_Data$Pos, 
                    Tm = SG_Data$Tm, 
                    Age = SG_Data$Age, 
                    Age.Diff = SG_Data$Age.Diff, 
                    G = SG_Data$G, 
                    G.Diff = SG_Data$G.Diff, 
                    GS = SG_Data$GS, 
                    GS.Diff = SG_Data$GS.Diff
                    )

SG_Data_G <- SG_Data_G %>%
  select(Player, Pos, Tm, Age, Age.Diff, G, G.Diff, GS, GS.Diff, MP, MP.Diff, FG, FG.Diff, FGA, FGA.Diff, X3P, X3P.Diff, X3PA, X3PA.Diff, X2P, X2P.Diff, X2PA, X2PA.Diff, FT, FT.Diff, FTA, FTA.Diff, TRB, TRB.Diff, AST, AST.Diff, STL, STL.Diff, BLK, BLK.Diff, TOV, TOV.Diff, PF, PF.Diff, PTS, PTS.Diff, FG_P, FG_P.Diff, FT_P, FT_P.Diff, X3P_P, X3P_P.Diff, X2P_P, X2P_P.Diff, eFG_P, eFG_P.Diff, ORB, ORB.Diff, DRB, DRB.Diff)
```

# SG Stats Per Minutes Played

```{r sg.mp, echo=FALSE}
#Creating a dataframe with the data divided by Minutes Played
SG_Filter_MP <- select(SG_Data,FG:DRB.Diff) 

SG_Stats_MP <- SG_Filter_MP %>% mutate_if(is.numeric, funs(./SG_Data$MP))

SG_Data_MP <- SG_Stats_MP %>%
            mutate(FG.Diff = abs(SG_Stats_MP$FG - median(SG_Stats_MP$FG)), 
                   FGA.Diff = abs(SG_Stats_MP$FGA - median(SG_Stats_MP$FGA)),
                   X3P.Diff = abs(SG_Stats_MP$X3P - median(SG_Stats_MP$X3P)),
                   X3PA.Diff = abs(SG_Stats_MP$X3PA- median(SG_Stats_MP$X3PA)),
                   X2P.Diff = abs(SG_Stats_MP$X2P - median(SG_Stats_MP$X2P)),
                   X2PA.Diff =abs(SG_Stats_MP$X2PA - median(SG_Stats_MP$X2PA)),
                   FT.Diff = abs(SG_Stats_MP$FT - median(SG_Stats_MP$FT)),
                   FTA.Diff =abs(SG_Stats_MP$FTA - median(SG_Stats_MP$FTA)),
                   TRB.Diff =abs(SG_Stats_MP$TRB - median(SG_Stats_MP$TRB)),
                   AST.Diff =abs(SG_Stats_MP$AST - median(SG_Stats_MP$AST)), 
                   STL.Diff =abs(SG_Stats_MP$STL - median(SG_Stats_MP$STL)), 
                   BLK.Diff =abs(SG_Stats_MP$BLK - median(SG_Stats_MP$BLK)),
                   TOV.Diff =abs(SG_Stats_MP$TOV - median(SG_Stats_MP$TOV)),
                   PF.Diff =abs(SG_Stats_MP$PF - median(SG_Stats_MP$PF)),
                   PTS.Diff =abs(SG_Stats_MP$PTS - median(SG_Stats_MP$PTS)),
                   FG_P.Diff =abs(SG_Stats_MP$FG_P - median(SG_Stats_MP$FG_P)),
                   FT_P.Diff =abs(SG_Stats_MP$FT_P - median(SG_Stats_MP$FT_P)),
                   X3P_P.Diff =abs(SG_Stats_MP$X3P_P - median(SG_Stats_MP$X3P_P)),
                   X2P_P.Diff =abs(SG_Stats_MP$X2P_P - median(SG_Stats_MP$X2P_P)),
                   eFG_P.Diff =abs(SG_Stats_MP$eFG_P - median(SG_Stats_MP$eFG_P)), 
                   ORB.Diff = abs(SG_Stats_MP$ORB - median(SG_Stats_MP$ORB)),
                   DRB.Diff = abs(SG_Stats_MP$DRB - median(SG_Stats_MP$DRB))
                   )
# Restructuring of Columns to make columns related to one another next to one another
SG_Data_MP <- mutate(SG_Data_MP, 
                    Player = SG_Data$Player, 
                    Pos = SG_Data$Pos, 
                    Tm = SG_Data$Tm, 
                    Age = SG_Data$Age, 
                    Age.Diff = SG_Data$Age.Diff, 
                    G = SG_Data$G, 
                    G.Diff = SG_Data$G.Diff, 
                    GS = SG_Data$GS, 
                    GS.Diff = SG_Data$GS.Diff,
                    MP = SG_Data$MP, 
                    MP.Diff = SG_Data$MP.Diff
                    )

SG_Data_MP <- SG_Data_MP %>%
  select(Player, Pos, Tm, Age, Age.Diff, G, G.Diff, GS, GS.Diff, MP, MP.Diff, FG, FG.Diff, FGA, FGA.Diff, X3P, X3P.Diff, X3PA, X3PA.Diff, X2P, X2P.Diff, X2PA, X2PA.Diff, FT, FT.Diff, FTA, FTA.Diff, TRB, TRB.Diff, AST, AST.Diff, STL, STL.Diff, BLK, BLK.Diff, TOV, TOV.Diff, PF, PF.Diff, PTS, PTS.Diff, FG_P, FG_P.Diff, FT_P, FT_P.Diff, X3P_P, X3P_P.Diff, X2P_P, X2P_P.Diff, eFG_P, eFG_P.Diff, ORB, ORB.Diff, DRB, DRB.Diff)
```

#Finding the Stats for SGs
SG_Data <- filter(BRTotal, Pos == "SG")

#Finding the Differences for each player from the averages
SG_Sum_G <- select(SG_Data, FG:PTS)
SG_Totals <- colSums(SG_Sum_G)

#Building the Dataframe of the Differences
SG_Avg_G <- SG_Totals / sum(SG_Data$G)
SG_Sum_G <- SG_Sum_G %>% mutate(abs(SG_Sum_G$FG - SG_Avg_G[1]), abs(FGA - SG_Avg_G[2]), abs(SG_Sum_G$X3P - SG_Avg_G[3]), abs(SG_Sum_G$X3PA- SG_Avg_G[4]), abs(SG_Sum_G$X2P - SG_Avg_G[5]), abs(SG_Sum_G$X2PA - SG_Avg_G[6]), abs(SG_Sum_G$FT - SG_Avg_G[7]), abs(SG_Sum_G$FTA - SG_Avg_G[8]), abs(SG_Sum_G$TRB - SG_Avg_G[9]), abs(SG_Sum_G$AST - SG_Avg_G[10]), abs(SG_Sum_G$STL - SG_Avg_G[11]), abs(SG_Sum_G$BLK - SG_Avg_G[12]), abs(SG_Sum_G$TOV - SG_Avg_G[13]), abs(SG_Sum_G$PTS - SG_Avg_G[14]))
SG_Diff_G <- select(SG_Sum_G, 15:28)
SG_Diff_G <- SG_Diff_G %>% mutate(rowSums(SG_Diff_G), SG_Data$Player, SG_Data$G, SG_Data$GS, SG_Data$Pos)
colnames(SG_Diff_G) = c("FG", "FGA", "3P", "3PA", "2P", "2PA", "FT", "FTA", "TRB", "AST", "STL", "BLK", "TOV", "PTS", "Total Difference", "Player", "G", "GS", "Pos")
SG_Diff_G <- select(SG_Diff_G, Player, `Total Difference`, G, GS, Pos)

#Building the Dataframe of the Differences for Minutes Played
SG_Sum_MP <- select(SG_Data,FG:PTS) 
SG_Totals_MP <- colSums(SG_Sum_MP)

SG_Avg_MP <- SG_Totals_MP / sum(SG_Data$MP)
SG_Sum_MP <- SG_Sum_MP %>% mutate(abs(SG_Sum_MP$FG - SG_Avg_MP[1]), abs(SG_Sum_MP$FGA - SG_Avg_MP[2]), abs(SG_Sum_MP$X3P - SG_Avg_MP[3]), abs(SG_Sum_MP$X3PA- SG_Avg_MP[4]), abs(SG_Sum_MP$X2P - SG_Avg_MP[5]), abs(SG_Sum_MP$X2PA - SG_Avg_MP[6]), abs(SG_Sum_MP$FT - SG_Avg_MP[7]), abs(SG_Sum_MP$FTA - SG_Avg_MP[8]), abs(SG_Sum_MP$TRB - SG_Avg_MP[9]), abs(SG_Sum_MP$AST - SG_Avg_MP[10]), abs(SG_Sum_MP$STL - SG_Avg_MP[11]), abs(SG_Sum_MP$BLK - SG_Avg_MP[12]), abs(SG_Sum_MP$TOV - SG_Avg_MP[13]), abs(SG_Sum_MP$PTS - SG_Avg_MP[14]))
SG_Diff_MP <- select(SG_Sum_MP, 15:28)
SG_Diff_MP <- SG_Diff_MP %>% mutate(rowSums(SG_Diff_MP), SG_Data$Player, SG_Data$MP, SG_Data$Pos)
colnames(SG_Diff_MP) = c("FG", "FGA", "3P", "3PA", "2P", "2PA", "FT", "FTA", "TRB", "AST", "STL", "BLK", "TOV", "PTS", "Total Difference", "Player", "MP", "Pos")
SG_Diff_MP <- select(SG_Diff_MP, Player, `Total Difference`, MP, Pos)

#Finding the Stats for SFs
SF_Data <- filter(BRTotal, Pos == "SF")

#Finding the Differences for each player from the averages
SF_Sum_G <- select(SF_Data, FG:PTS)
SF_Totals <- colSums(SF_Sum_G)

#Building the Dataframe of the Differences
SF_Avg_G <- SF_Totals / sum(SF_Data$G)
SF_Sum_G <- SF_Sum_G %>% mutate(abs(SF_Sum_G$FG - SF_Avg_G[1]), abs(SF_Sum_G$FGA - SF_Avg_G[2]), abs(SF_Sum_G$X3P - SF_Avg_G[3]), abs(SF_Sum_G$X3PA- SF_Avg_G[4]), abs(SF_Sum_G$X2P - SF_Avg_G[5]), abs(SF_Sum_G$X2PA - SF_Avg_G[6]), abs(SF_Sum_G$FT - SF_Avg_G[7]), abs(SF_Sum_G$FTA - SF_Avg_G[8]), abs(SF_Sum_G$TRB - SF_Avg_G[9]), abs(SF_Sum_G$AST - SF_Avg_G[10]), abs(SF_Sum_G$STL - SF_Avg_G[11]), abs(SF_Sum_G$BLK - SF_Avg_G[12]), abs(SF_Sum_G$TOV - SF_Avg_G[13]), abs(SF_Sum_G$PTS - SF_Avg_G[14]))
SF_Diff_G <- select(SF_Sum_G, 15:28)
SF_Diff_G <- SF_Diff_G %>% mutate(rowSums(SF_Diff_G), SF_Data$Player, SF_Data$G, SF_Data$GS, SF_Data$Pos)
colnames(SF_Diff_G) = c("FG", "FGA", "3P", "3PA", "2P", "2PA", "FT", "FTA", "TRB", "AST", "STL", "BLK", "TOV", "PTS", "Total Difference", "Player", "G", "GS", "Pos")
SF_Diff_G <- select(SF_Diff_G, Player, `Total Difference`, G, GS, Pos)

#Building the Dataframe of the Differences for Minutes Played
SF_Sum_MP <- select(SF_Data,FG:PTS) 
SF_Totals_MP <- colSums(SF_Sum_MP)

SF_Avg_MP <- SF_Totals_MP / sum(SF_Data$MP)
SF_Sum_MP <- SF_Sum_MP %>% mutate(abs(SF_Sum_MP$FG - SF_Avg_MP[1]), abs(SF_Sum_MP$FGA - SF_Avg_MP[2]), abs(SF_Sum_MP$X3P - SF_Avg_MP[3]), abs(SF_Sum_MP$X3PA- SF_Avg_MP[4]), abs(SF_Sum_MP$X2P - SF_Avg_MP[5]), abs(SF_Sum_MP$X2PA - SF_Avg_MP[6]), abs(SF_Sum_MP$FT - SF_Avg_MP[7]), abs(SF_Sum_MP$FTA - SF_Avg_MP[8]), abs(SF_Sum_MP$TRB - SF_Avg_MP[9]), abs(SF_Sum_MP$AST - SF_Avg_MP[10]), abs(SF_Sum_MP$STL - SF_Avg_MP[11]), abs(SF_Sum_MP$BLK - SF_Avg_MP[12]), abs(SF_Sum_MP$TOV - SF_Avg_MP[13]), abs(SF_Sum_MP$PTS - SF_Avg_MP[14]))
SF_Diff_MP <- select(SF_Sum_MP, 15:28)
SF_Diff_MP <- SF_Diff_MP %>% mutate(rowSums(SF_Diff_MP), SF_Data$Player, SF_Data$MP, SF_Data$Pos)
colnames(SF_Diff_MP) = c("FG", "FGA", "3P", "3PA", "2P", "2PA", "FT", "FTA", "TRB", "AST", "STL", "BLK", "TOV", "PTS", "Total Difference", "Player", "MP", "Pos")
SF_Diff_MP <- select(SF_Diff_MP, Player, `Total Difference`, MP, Pos)

#Finding the Stats for PFs
PF_Data <- filter(BRTotal, Pos == "PF")

#Finding the Differences for each player from the averages
PF_Sum_G <- select(PF_Data, FG:PTS)
PF_Totals <- colSums(PF_Sum_G)

#Building the Dataframe of the Differences
PF_Avg_G <- PF_Totals / sum(PF_Data$G)
PF_Sum_G <- PF_Sum_G %>% mutate(abs(PF_Sum_G$FG - PF_Avg_G[1]), abs(PF_Sum_G$FGA - PF_Avg_G[2]), abs(PF_Sum_G$X3P - PF_Avg_G[3]), abs(PF_Sum_G$X3PA- PF_Avg_G[4]), abs(PF_Sum_G$X2P - PF_Avg_G[5]), abs(PF_Sum_G$X2PA - PF_Avg_G[6]), abs(PF_Sum_G$FT - PF_Avg_G[7]), abs(PF_Sum_G$FTA - PF_Avg_G[8]), abs(PF_Sum_G$TRB - PF_Avg_G[9]), abs(PF_Sum_G$AST - PF_Avg_G[10]), abs(PF_Sum_G$STL - PF_Avg_G[11]), abs(PF_Sum_G$BLK - PF_Avg_G[12]), abs(PF_Sum_G$TOV - PF_Avg_G[13]), abs(PF_Sum_G$PTS - PF_Avg_G[14]))
PF_Diff_G <- select(PF_Sum_G, 15:28)
PF_Diff_G <- PF_Diff_G %>% mutate(rowSums(PF_Diff_G), PF_Data$Player, PF_Data$G, PF_Data$GS, PF_Data$Pos)
colnames(PF_Diff_G) = c("FG", "FGA", "3P", "3PA", "2P", "2PA", "FT", "FTA", "TRB", "AST", "STL", "BLK", "TOV", "PTS", "Total Difference", "Player", "G", "GS", "Pos")
PF_Diff_G <- select(PF_Diff_G, Player, `Total Difference`, G, GS, Pos)

#Building the Dataframe of the Differences for Minutes Played
PF_Sum_MP <- select(PF_Data,FG:PTS) 
PF_Totals_MP <- colSums(PF_Sum_MP)

PF_Avg_MP <- PF_Totals_MP / sum(PF_Data$MP)
PF_Sum_MP <- PF_Sum_MP %>% mutate(abs(PF_Sum_MP$FG - PF_Avg_MP[1]), abs(PF_Sum_MP$FGA - PF_Avg_MP[2]), abs(PF_Sum_MP$X3P - PF_Avg_MP[3]), abs(PF_Sum_MP$X3PA- PF_Avg_MP[4]), abs(PF_Sum_MP$X2P - PF_Avg_MP[5]), abs(PF_Sum_MP$X2PA - PF_Avg_MP[6]), abs(PF_Sum_MP$FT - PF_Avg_MP[7]), abs(PF_Sum_MP$FTA - PF_Avg_MP[8]), abs(PF_Sum_MP$TRB - PF_Avg_MP[9]), abs(PF_Sum_MP$AST - PF_Avg_MP[10]), abs(PF_Sum_MP$STL - PF_Avg_MP[11]), abs(PF_Sum_MP$BLK - PF_Avg_MP[12]), abs(PF_Sum_MP$TOV - PF_Avg_MP[13]), abs(PF_Sum_MP$PTS - PF_Avg_MP[14]))
PF_Diff_MP <- select(PF_Sum_MP, 15:28)
PF_Diff_MP <- PF_Diff_MP %>% mutate(rowSums(PF_Diff_MP), PF_Data$Player, PF_Data$MP, PF_Data$Pos)
colnames(PF_Diff_MP) = c("FG", "FGA", "3P", "3PA", "2P", "2PA", "FT", "FTA", "TRB", "AST", "STL", "BLK", "TOV", "PTS", "Total Difference", "Player", "MP", "Pos")
PF_Diff_MP <- select(PF_Diff_MP, Player, `Total Difference`, MP, Pos)


#Finding the Stats for Cs
C_Data  <- filter(BRTotal, Pos == "C")

#Finding the Differences for each player from the averages
C_Sum_G <- select(C_Data, FG:PTS)
C_Totals <- colSums(C_Sum_G)

#Building the Dataframe of the Differences
C_Avg_G <- C_Totals / sum(C_Data$G)
C_Sum_G <- C_Sum_G %>% mutate(abs(C_Sum_G$FG - C_Avg_G[1]), abs(C_Sum_G$FGA - C_Avg_G[2]), abs(C_Sum_G$X3P - C_Avg_G[3]), abs(C_Sum_G$X3PA- C_Avg_G[4]), abs(C_Sum_G$X2P - C_Avg_G[5]), abs(C_Sum_G$X2PA - C_Avg_G[6]), abs(C_Sum_G$FT - C_Avg_G[7]), abs(C_Sum_G$FTA - C_Avg_G[8]), abs(C_Sum_G$TRB - C_Avg_G[9]), abs(C_Sum_G$AST - C_Avg_G[10]), abs(C_Sum_G$STL - C_Avg_G[11]), abs(C_Sum_G$BLK - C_Avg_G[12]), abs(C_Sum_G$TOV - C_Avg_G[13]), abs(C_Sum_G$PTS - C_Avg_G[14]))
C_Diff_G <- select(C_Sum_G, 15:28)
C_Diff_G <- C_Diff_G %>% mutate(rowSums(C_Diff_G), C_Data$Player, C_Data$G, C_Data$GS, C_Data$Pos)
colnames(C_Diff_G) = c("FG", "FGA", "3P", "3PA", "2P", "2PA", "FT", "FTA", "TRB", "AST", "STL", "BLK", "TOV", "PTS", "Total Difference", "Player", "G", "GS", "Pos")
C_Diff_G <- select(C_Diff_G, Player, `Total Difference`, G, GS, Pos)

#Building the Dataframe of the Differences for Minutes Played
C_Sum_MP <- select(C_Data,FG:PTS) 
C_Totals_MP <- colSums(C_Sum_MP)

C_Avg_MP <- C_Totals_MP / sum(C_Data$MP)
C_Sum_MP <- C_Sum_MP %>% mutate(abs(C_Sum_MP$FG - C_Avg_MP[1]), abs(C_Sum_MP$FGA - C_Avg_MP[2]), abs(C_Sum_MP$X3P - C_Avg_MP[3]), abs(C_Sum_MP$X3PA- C_Avg_MP[4]), abs(C_Sum_MP$X2P - C_Avg_MP[5]), abs(C_Sum_MP$X2PA - C_Avg_MP[6]), abs(C_Sum_MP$FT - C_Avg_MP[7]), abs(C_Sum_MP$FTA - C_Avg_MP[8]), abs(C_Sum_MP$TRB - C_Avg_MP[9]), abs(C_Sum_MP$AST - C_Avg_MP[10]), abs(C_Sum_MP$STL - C_Avg_MP[11]), abs(C_Sum_MP$BLK - C_Avg_MP[12]), abs(C_Sum_MP$TOV - C_Avg_MP[13]), abs(C_Sum_MP$PTS - C_Avg_MP[14]))
C_Diff_MP <- select(C_Sum_MP, 15:28)
C_Diff_MP <- C_Diff_MP %>% mutate(rowSums(C_Diff_MP), C_Data$Player, C_Data$MP, C_Data$Pos)
colnames(C_Diff_MP) = c("FG", "FGA", "3P", "3PA", "2P", "2PA", "FT", "FTA", "TRB", "AST", "STL", "BLK", "TOV", "PTS", "Total Difference", "Player", "MP", "Pos")
C_Diff_MP <- select(C_Diff_MP, Player, `Total Difference`, MP, Pos)


#Total Diff

#Games
G_Diff <- rbind(PG_Diff_G, SG_Diff_G)
G_Diff <- rbind(G_Diff, SF_Diff_G)
G_Diff <- rbind(G_Diff, PF_Diff_G)
G_Diff <- rbind(G_Diff, C_Diff_G)

#Minutes
MP_Diff <- rbind(PG_Diff_MP, SG_Diff_MP)
MP_Diff <- rbind(MP_Diff, SF_Diff_MP)
MP_Diff <- rbind(MP_Diff, PF_Diff_MP)
MP_Diff <- rbind(MP_Diff, C_Diff_MP)
```

## PG Data

While this data is skewed right, since the sample size is 97, we will still perform statisitical analysis on this data. 
```{r, echo=T, warning=FALSE, message=TRUE}
ggplot(PG_Diff_G, aes(x = `Total Difference`)) + geom_histogram(binwidth = 500, fill = "aquamarine3", col = "black") 

ggplot(PG_Diff_MP, aes(x = `Total Difference`)) + geom_histogram(binwidth = 500, fill = "aquamarine3", col = "black") 
```

```{r, echo=T, warning=FALSE, message=TRUE}
#PG_Diff_G %>% select(Player, `Total Difference`) %>% arrange(desc(`Total Difference`))
```



## SG Data
```{r, echo=T, warning=FALSE, message=TRUE}
ggplot(SG_Diff_G, aes(x = `Total Difference`)) + geom_histogram(binwidth = 500, fill = "orchid2", col = "black") 

ggplot(SG_Diff_MP, aes(x = `Total Difference`)) + geom_histogram(binwidth = 500, fill = "orchid2", col = "black") 
```



## SF Data
```{r, echo=T, warning=FALSE, message=TRUE}
ggplot(SF_Diff_G, aes(x = `Total Difference`)) + geom_histogram(binwidth = 500, fill = "dodgerblue2", col = "black") 

ggplot(SF_Diff_MP, aes(x = `Total Difference`)) + geom_histogram(binwidth = 500, fill = "dodgerblue2", col = "black") 
```


## PF Data
```{r, echo=T, warning=FALSE, message=TRUE}
ggplot(PF_Diff_G, aes(x = `Total Difference`)) + geom_histogram(binwidth = 500, fill = "darkgoldenrod3", col = "black") 

ggplot(PF_Diff_MP, aes(x = `Total Difference`)) + geom_histogram(binwidth = 500, fill = "darkgoldenrod3", col = "black") 
```


## C Data
```{r, echo=T, warning=FALSE, message=TRUE}
ggplot(C_Diff_G, aes(x = `Total Difference`)) + geom_histogram(binwidth = 500, fill = "coral1", col = "black") 

ggplot(C_Diff_MP, aes(x = `Total Difference`)) + geom_histogram(binwidth = 500, fill = "coral1", col = "black") 
```



The average difference
```{r, echo=T, warning=FALSE, message=TRUE}
summary(PG_Diff_G$`Total Difference`)

ggplot(PG_Diff_G, aes(x = G, y = `Total Difference`, label = Player)) + geom_text(aes(label = Player), size = 2)

hist(PG_Diff_G$`Total Difference`)
```

Only Outliers
```{r, echo=T, warning=FALSE, message=TRUE}
#M = mean(PG_Diff_G$`Total Difference`)
#S = sd(PG_Diff_G$`Total Difference`)
#PG_Diff_G %>% filter(`Total Difference` > M + 2*S) 
```

## Total Data
Averages
```{R, echo=T,  warning=FALSE, message=TRUE}
PG_Avg_G
SG_Avg_G
SF_Avg_G
PF_Avg_G
C_Avg_G

PG_Avg_MP
SG_Avg_MP
SF_Avg_MP
PF_Avg_MP
C_Avg_MP
```

Average of the difference for all positions
```{r, echo=T, warning=FALSE, message=TRUE}

ggplot(G_Diff, aes(x = `Total Difference`, color = Pos)) + geom_histogram(binwidth = 500, fill="white", alpha=0.5, position="identity")

#Games
ggplot(G_Diff, aes(G, `Total Difference`, label = rownames(Player))) + geom_text(aes(label = Player, color = Pos), hjust = - 0.5, size = 2, check_overlap = TRUE) + geom_smooth(method="glm", se=FALSE, color = "black")

#Minutes
ggplot(MP_Diff, aes(MP, `Total Difference`, label = rownames(Player))) + geom_text(aes(label = Player, color = Pos), hjust = - 0.5, size = 2, check_overlap = TRUE) + geom_smooth(method="glm", se=FALSE, color = "black")
```


Who are the most average players across all statistics?
```{r, echo=T, warning=FALSE, message=TRUE}
head(arrange(G_Diff, `Total Difference`))
```

Excluding players who have played less than 20 games
```{r, echo=T, warning=FALSE, message=TRUE}
head(arrange(filter(G_Diff, G_Diff$G >= 20), `Total Difference`)) 
```

Assuming starters will play 75% of games (excluding injury) here are the most average starters
```{r, echo=T, warning=FALSE, message=TRUE}
head(arrange(filter(G_Diff, G_Diff$GS / G_Diff$G > 0.75), `Total Difference`)) 
```



