---
title: "Average Player"
author: "David Roycroft"
date: "2/12/2021"
output: pdf_document
---

```{r setup, include=FALSE}
library(readr)
library(tidyverse)

#Setting Working Directory
setwd("C:\\Users\\Sherlock\\Documents\\R Projects\\NBA")

BRTotal <- read.csv("2019_20_BRTotal.csv")
BRTotal <- rename(BRTotal, Player = ï..Player)
AverageData  <- select(BRTotal, Player, Pos, Tm, G, FG, FGA, X3P, X3PA, X2P, X2PA, FT, FTA, TRB, AST, STL, BLK, TOV, PTS)

#Finding the Stats for PGs
PG_Data <- filter(AverageData, Pos == "PG")

#Finding the Differences for each player from the averages
PG_Sum_G <- select(PG_Data,FG:PTS) 
PG_Totals <- colSums(PG_Sum_G)

#Building the Dataframe of the Differences for Games Played
PG_Avg_G <- PG_Totals / sum(PG_Data$G)
PG_Sum_G <- PG_Sum_G %>% mutate(abs(PG_Sum_G$FG - PG_Avg_G[1]), abs(PG_Sum_G$FGA - PG_Avg_G[2]), abs(PG_Sum_G$X3P - PG_Avg_G[3]), abs(PG_Sum_G$X3PA- PG_Avg_G[4]), abs(PG_Sum_G$X2P - PG_Avg_G[5]), abs(PG_Sum_G$X2PA - PG_Avg_G[6]), abs(PG_Sum_G$FT - PG_Avg_G[7]), abs(PG_Sum_G$FTA - PG_Avg_G[8]), abs(PG_Sum_G$TRB - PG_Avg_G[9]), abs(PG_Sum_G$AST - PG_Avg_G[10]), abs(PG_Sum_G$STL - PG_Avg_G[11]), abs(PG_Sum_G$BLK - PG_Avg_G[12]), abs(PG_Sum_G$TOV - PG_Avg_G[13]), abs(PG_Sum_G$PTS - PG_Avg_G[14]))
PG_Diff_G <- select(PG_Sum_G, 15:28)
PG_Diff_G <- PG_Diff_G %>% mutate(rowSums(PG_Diff_G), PG_Data$Player, PG_Data$G, PG_Data$Pos)
colnames(PG_Diff_G) = c("FG", "FGA", "3P", "3PA", "2P", "2PA", "FT", "FTA", "TRB", "AST", "STL", "BLK", "TOV", "PTS", "Total Difference", "Player", "G", "Pos")
PG_Diff_G <- select(PG_Diff_G, Player, `Total Difference`, G, Pos)

#Finding the Stats for SGs
SG_Data <- filter(AverageData, Pos == "SG")

#Finding the Differences for each player from the averages
SG_Sum_G <- select(SG_Data, FG:PTS)
SG_Totals <- colSums(SG_Sum_G)

#Building the Dataframe of the Differences
SG_Avg_G <- SG_Totals / sum(SG_Data$G)
SG_Sum_G <- SG_Sum_G %>% mutate(abs(SG_Sum_G$FG - SG_Avg_G[1]), abs(FGA - SG_Avg_G[2]), abs(SG_Sum_G$X3P - SG_Avg_G[3]), abs(SG_Sum_G$X3PA- SG_Avg_G[4]), abs(SG_Sum_G$X2P - SG_Avg_G[5]), abs(SG_Sum_G$X2PA - SG_Avg_G[6]), abs(SG_Sum_G$FT - SG_Avg_G[7]), abs(SG_Sum_G$FTA - SG_Avg_G[8]), abs(SG_Sum_G$TRB - SG_Avg_G[9]), abs(SG_Sum_G$AST - SG_Avg_G[10]), abs(SG_Sum_G$STL - SG_Avg_G[11]), abs(SG_Sum_G$BLK - SG_Avg_G[12]), abs(SG_Sum_G$TOV - SG_Avg_G[13]), abs(SG_Sum_G$PTS - SG_Avg_G[14]))
SG_Diff_G <- select(SG_Sum_G, 15:28)
SG_Diff_G <- SG_Diff_G %>% mutate(rowSums(SG_Diff_G), SG_Data$Player, SG_Data$G, SG_Data$Pos)
colnames(SG_Diff_G) = c("FG", "FGA", "3P", "3PA", "2P", "2PA", "FT", "FTA", "TRB", "AST", "STL", "BLK", "TOV", "PTS", "Total Difference", "Player", "G", "Pos")
SG_Diff_G <- select(SG_Diff_G, Player, `Total Difference`, G, Pos)

#Finding the Stats for SFs
SF_Data <- filter(AverageData, Pos == "SF")

#Finding the Differences for each player from the averages
SF_Sum_G <- select(SF_Data, FG:PTS)
SF_Totals <- colSums(SF_Sum_G)

#Building the Dataframe of the Differences
SF_Avg_G <- SF_Totals / sum(SF_Data$G)
SF_Sum_G <- SF_Sum_G %>% mutate(abs(SF_Sum_G$FG - SF_Avg_G[1]), abs(SF_Sum_G$FGA - SF_Avg_G[2]), abs(SF_Sum_G$X3P - SF_Avg_G[3]), abs(SF_Sum_G$X3PA- SF_Avg_G[4]), abs(SF_Sum_G$X2P - SF_Avg_G[5]), abs(SF_Sum_G$X2PA - SF_Avg_G[6]), abs(SF_Sum_G$FT - SF_Avg_G[7]), abs(SF_Sum_G$FTA - SF_Avg_G[8]), abs(SF_Sum_G$TRB - SF_Avg_G[9]), abs(SF_Sum_G$AST - SF_Avg_G[10]), abs(SF_Sum_G$STL - SF_Avg_G[11]), abs(SF_Sum_G$BLK - SF_Avg_G[12]), abs(SF_Sum_G$TOV - SF_Avg_G[13]), abs(SF_Sum_G$PTS - SF_Avg_G[14]))
SF_Diff_G <- select(SF_Sum_G, 15:28)
SF_Diff_G <- SF_Diff_G %>% mutate(rowSums(SF_Diff_G), SF_Data$Player, SF_Data$G, SF_Data$Pos)
colnames(SF_Diff_G) = c("FG", "FGA", "3P", "3PA", "2P", "2PA", "FT", "FTA", "TRB", "AST", "STL", "BLK", "TOV", "PTS", "Total Difference", "Player", "G", "Pos")
SF_Diff_G <- select(SF_Diff_G, Player, `Total Difference`, G, Pos)

#Finding the Stats for PFs
PF_Data <- filter(AverageData, Pos == "PF")

#Finding the Differences for each player from the averages
PF_Sum_G <- select(PF_Data, FG:PTS)
PF_Totals <- colSums(PF_Sum_G)

#Building the Dataframe of the Differences
PF_Avg_G <- PF_Totals / sum(PF_Data$G)
PF_Sum_G <- PF_Sum_G %>% mutate(abs(PF_Sum_G$FG - PF_Avg_G[1]), abs(PF_Sum_G$FGA - PF_Avg_G[2]), abs(PF_Sum_G$X3P - PF_Avg_G[3]), abs(PF_Sum_G$X3PA- PF_Avg_G[4]), abs(PF_Sum_G$X2P - PF_Avg_G[5]), abs(PF_Sum_G$X2PA - PF_Avg_G[6]), abs(PF_Sum_G$FT - PF_Avg_G[7]), abs(PF_Sum_G$FTA - PF_Avg_G[8]), abs(PF_Sum_G$TRB - PF_Avg_G[9]), abs(PF_Sum_G$AST - PF_Avg_G[10]), abs(PF_Sum_G$STL - PF_Avg_G[11]), abs(PF_Sum_G$BLK - PF_Avg_G[12]), abs(PF_Sum_G$TOV - PF_Avg_G[13]), abs(PF_Sum_G$PTS - PF_Avg_G[14]))
PF_Diff_G <- select(PF_Sum_G, 15:28)
PF_Diff_G <- PF_Diff_G %>% mutate(rowSums(PF_Diff_G), PF_Data$Player, PF_Data$G, PF_Data$Pos)
colnames(PF_Diff_G) = c("FG", "FGA", "3P", "3PA", "2P", "2PA", "FT", "FTA", "TRB", "AST", "STL", "BLK", "TOV", "PTS", "Total Difference", "Player", "G", "Pos")
PF_Diff_G <- select(PF_Diff_G, Player, `Total Difference`, G, Pos)

#Finding the Stats for Cs
C_Data  <- filter(AverageData, Pos == "C")

#Finding the Differences for each player from the averages
C_Sum_G <- select(C_Data, FG:PTS)
C_Totals <- colSums(C_Sum_G)

#Building the Dataframe of the Differences
C_Avg_G <- C_Totals / sum(C_Data$G)
C_Sum_G <- C_Sum_G %>% mutate(abs(C_Sum_G$FG - C_Avg_G[1]), abs(C_Sum_G$FGA - C_Avg_G[2]), abs(C_Sum_G$X3P - C_Avg_G[3]), abs(C_Sum_G$X3PA- C_Avg_G[4]), abs(C_Sum_G$X2P - C_Avg_G[5]), abs(C_Sum_G$X2PA - C_Avg_G[6]), abs(C_Sum_G$FT - C_Avg_G[7]), abs(C_Sum_G$FTA - C_Avg_G[8]), abs(C_Sum_G$TRB - C_Avg_G[9]), abs(C_Sum_G$AST - C_Avg_G[10]), abs(C_Sum_G$STL - C_Avg_G[11]), abs(C_Sum_G$BLK - C_Avg_G[12]), abs(C_Sum_G$TOV - C_Avg_G[13]), abs(C_Sum_G$PTS - C_Avg_G[14]))
C_Diff_G <- select(C_Sum_G, 15:28)
C_Diff_G <- C_Diff_G %>% mutate(rowSums(C_Diff_G), C_Data$Player, C_Data$G, C_Data$Pos)
colnames(C_Diff_G) = c("FG", "FGA", "3P", "3PA", "2P", "2PA", "FT", "FTA", "TRB", "AST", "STL", "BLK", "TOV", "PTS", "Total Difference", "Player", "G", "Pos")
C_Diff_G <- select(C_Diff_G, Player, `Total Difference`, G, Pos)

#Total Diff
G_Diff <- rbind(PG_Diff_G, SG_Diff_G)
G_Diff <- rbind(G_Diff, SF_Diff_G)
G_Diff <- rbind(G_Diff, PF_Diff_G)
G_Diff <- rbind(G_Diff, C_Diff_G)
```

## PG Data

While this data is skewed right, since the sample size is 97, we will still perform statisitical analysis on this data. 
```{r, echo=FALSE}
ggplot(PG_Diff_G, aes(x = `Total Difference`)) + geom_histogram(binwidth = 500, fill = "aquamarine3", col = "black") 
```

```{r, echo=FALSE}
#PG_Diff_G %>% select(Player, `Total Difference`) %>% arrange(desc(`Total Difference`))
```



## SG Data
```{r, echo=FALSE}
ggplot(SG_Diff_G, aes(x = `Total Difference`)) + geom_histogram(binwidth = 500, fill = "orchid2", col = "black") 
```



## SF Data
```{r, echo=FALSE}
ggplot(SG_Diff_G, aes(x = `Total Difference`)) + geom_histogram(binwidth = 500, fill = "dodgerblue2", col = "black") 
```


## PF Data
```{r, echo=FALSE}
ggplot(SG_Diff_G, aes(x = `Total Difference`)) + geom_histogram(binwidth = 500, fill = "darkgoldenrod3", col = "black") 
```


## C Data
```{r, echo=FALSE}
ggplot(SG_Diff_G, aes(x = `Total Difference`)) + geom_histogram(binwidth = 500, fill = "coral1", col = "black") 
```



The average difference
```{r, echo=F}
summary(PG_Diff_G$`Total Difference`)

ggplot(PG_Diff_G, aes(x = G, y = `Total Difference`, label = Player)) + geom_text(aes(label = Player), size = 2)

hist(PG_Diff_G$`Total Difference`)
```

Only Outliers
```{r, echo=FALSE}
M = mean(PG_Diff_G$`Total Difference`)
S = sd(PG_Diff_G$`Total Difference`)
PG_Diff_G %>% filter(`Total Difference` > M + 2*S) 
```

## Total Data
Average of the difference for all positions
```{r, echo=F, warning=FALSE}
mu = mean(G_Diff$`Total Difference`)
hist(G_Diff$`Total Difference`)

ggplot(G_Diff, aes(x = `Total Difference`, color = Pos)) + geom_histogram(binwidth = 500, fill="white", alpha=0.5, position="identity")


ggplot(G_Diff, aes(G, `Total Difference`, label = rownames(Player))) + geom_text(aes(label = Player, color = Pos), hjust = - 0.5, size = 2, check_overlap = TRUE) + geom_smooth(method="glm", se=FALSE, color = "black")
```


Who are the most average players across all statistics?
```{r, echo=FALSE}
head(arrange(G_Diff, `Total Difference`))
```

Excluding players who have played less than 20 games
```{r, echo=FALSE}
head(arrange(filter(G_Diff, G_Diff$G >= 20), `Total Difference`)) 
```

Assuming starters will play 75% of games (excluding injury) here are the most average starters
```{r, echo=FALSE}
head(arrange(filter(G_Diff, G_Diff$G >= 70), `Total Difference`)) 
```











